manuscript_figures

### 2024-06-28 scripts/manuscript_figures.Rmd
updated table output for permanova and simper

@@

>>>>

# Create dataframe from PERMANOVA results
permanova_df <- data.frame(
  Factor = c("SITE", "YEAR", "Residual", "Total"),
  Df = c(1, 4, 37, 42),
  SumOfSqs = c(0.2632, 2.8619, 7.4000, 10.5251),
  R2 = c(0.02501, 0.27191, 0.70308, 1.00000),
  F = c(1.3160, 3.5774, NA, NA),
  Pr_F = c(0.235, 0.001, NA, NA)  # Changed column name to Pr_F
)

# Create flextable object
flex_perm <- flextable(permanova_df)

# Customize the flextable
flex_perm <- flex_perm %>%
  set_header_labels(
    Factor = "Factor",
    Df = "Df",
    SumOfSqs = "Sum of Squares",
    R2 = "R2",
    F = "F",
    Pr_F = "Pr(>F)"  # Changed to match the new column name
  ) %>%
  colformat_double(digits = 4) %>%
  bold(i = ~ Factor == "YEAR", j = "Pr_F") %>%  # Changed to match the new column name
  add_header_lines(values = c(
    "Permutation test for adonis under reduced model",
    "Terms added sequentially (first to last)",
    "Permutation: free",
    "Number of permutations: 999"
  )) %>%
  add_footer_lines(c(
    "Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1",
    "adonis2(formula = community_data ~ SITE + YEAR, data = environmental_data, permutations = 999, method = \"bray\")"
  )) %>%
  autofit() %>%
  theme_box()

# Save flextable as PNG
png_file <- "output/model.result.tables/permanova.png"
save_as_image(flex_perm, path = png_file)

@@

# Create dataframe from SIMPER results
simp <- data.frame(
  Species = rownames(summary(simper_result)$`Fort Wetherill_King's Beach`),
  Average = summary(simper_result)$`Fort Wetherill_King's Beach`$average,
  Ratio = summary(simper_result)$`Fort Wetherill_King's Beach`$ratio,
  Fort_Wetherill = summary(simper_result)$`Fort Wetherill_King's Beach`$ava,
  Kings_Beach = summary(simper_result)$`Fort Wetherill_King's Beach`$avb,
  Cumulative_Sum = summary(simper_result)$`Fort Wetherill_King's Beach`$cumsum,
  p_value = summary(simper_result)$`Fort Wetherill_King's Beach`$p
)

# Customize the flextable
flex_simp <- flex_simp %>%
  set_header_labels(
    Species = "Species",
    Average = "Avg. Contribution",
    Ratio = "Ratio",
    Fort_Wetherill = "Fort Wetherill Abundance",
    Kings_Beach = "King's Beach Abundance",
    Cumulative_Sum = "Cumulative Sum",
    p_value = "p-value"
  ) %>%
  autofit() %>%
  theme_box()

# Save flextable as PNG
png_file <- "output/model.result.tables/simper_results.png"
save_as_image(flex_simp, path = png_file)
